{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-08-18 paper/tex/sections/results.tex
update text to match in uncertainty section

\paragraph{Time since formation} 
In Fig.~\ref{fig:fiducial_pdf_distributions}e we show how long ago the DCOs detectable by LISA formed. For comparison we show the star formation history we have assumed in our Milky Way model (grey line). Star formation was highest at early times $6-12\unit{Gyr}$ ago, after which it declined.  In contrast, the DCOs detectable by LISA primarily formed in the relatively \textit{recent} history of our Milky Way, about $2 \unit{Gyr}$ ago. This reflects the fact that binaries in our simulation typically take about a Gyr to merge, a result as is commonly found also in other population synthesis studies.

@@

\subsection{Progenitors and formation channel \label{sec:progenitors_and_formation}}
\todo{for tom: Refer to appendix figure on formation channel and birth initial mass, mass ratio metallicity (and separation).}

@@

{\bf SdM: proposed to add this paragraph and plot. Draft text provided}
In Fig.~X we show the cumulative distribution of SNR expected together with the $1$ and $2\sigma$ uncertainties. We assumed a detection threshold of {\bf 8}. Of the total number of 140 {\bf check} detections SNRs larger than 10, 50, 100 respectively for 85, 16, and 9 sytems, where the high SNR systems are typically, but not only, the more massive BHBH systems.

{\bf Quote with errors. }

@@

We find that for a 4(10)-year LISA mission, approximately $\BHBHChirpMassMeasureableFour{}(\BHBHChirpMassMeasureableTen{})$ BHBHs, $\BHNSChirpMassMeasureableFour{}(\BHNSChirpMassMeasureableTen{})$ BHNSs and $\NSNSChirpMassMeasureableFour{}(\NSNSChirpMassMeasureableTen{})$ NSNSs have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the shaded region in Fig.~\ref{fig:m_c_unc}). Note that increasing the mission length significantly increases the number of detections for which we can measure the mass. This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.

@@

We plot the distribution of expected angular resolutions in Fig.~\ref{fig:ang_res}. We see that only {\bf x, x, and x\% [quote numbers pref. with errorbars] } of the sources can be resolved to an angular resolution better than 1 degree, for NSNS, BHNS and BHBH respectively. The fraction is higher for NSNS systems {\bf SdM: Do we understand why?}, which is will be of interest for counter part searches.

>>>>

\paragraph{Time since formation} 
In Fig.~\ref{fig:fiducial_pdf_distributions}e we show how long ago the DCOs detectable by LISA formed. For comparison we show the star formation history we have assumed in our Milky Way model (grey dotted line). Star formation was highest at early times $6-12\unit{Gyr}$ ago, after which it declined.  In contrast, the DCOs detectable by LISA primarily formed in the relatively \textit{recent} history of our Milky Way, about $2 \unit{Gyr}$ ago. This reflects the fact that binaries in our simulation typically take about a Gyr to merge, a result as is commonly found also in other population synthesis studies.

@@

\subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}
\todo{for tom: Refer to appendix figure on formation channel and birth initial mass, mass ratio metallicity (and separation).}

@@

In Fig.~\ref{fig:snr_dist} we show the cumulative number of detections with a given SNR. Although many have SNRs around the our assumed detection threshold of 7, many systems are detection with very high SNRs. We find that for a 4(10)-year LISA mission, of the 124(202) detections, 85(138), 16(27) and 9(14) systems have SNRs greater than 10, 50 and 100 respectively. These high SNR systems are typically, but not only, the more massive BHBH systems.

@@

We find that for a 4(10)-year LISA mission, approximately 41(105) detections have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the dark shaded region in Fig.~\ref{fig:m_c_unc}) whilst 13(31) have chirp mass uncertainties below 10\%. This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.

Note that increasing the mission length significantly increases the number of detections for which we can measure the mass. The total number of detections only scales as $\sqrt{T_{\rm obs}}$, yet we find that the total number of detections \textit{with well measured masses} scales approximately as $T_{\rm obs}$.

@@

We plot the distribution of expected angular resolutions in Fig.~\ref{fig:ang_res}. We see that, for a 4(10)-year LISA mission, approximately 82(123) sources can be resolved to an angular resolution better than 10 degrees and only 16(23) better than 1 degree.
